---
title: "Teletherapy and Online Self-Help - Updated"
output:
  html_document: default
  pdf_document: default
---

```{r, include = F}
####  Setup  ####
library(easypackages)
libraries("tidyverse", "ggplot2", "readr", "magrittr", "Amelia", "scales", "questionr", "corrplot", "knitr", "kableExtra", "conflicted")
walk(c("filter", "select", "count", "group_by"), ~ conflict_prefer(., "dplyr"))

rm(list = ls())

opts_chunk$set(echo = F, message = F)



####  Load Data  ####
raw <- read_rds("G:\\Shared drives\\Psychology_JSLab\\Projects\\In_Progress\\SBU_COVID19_Study\\Clean Data\\SBU COVID-19 Survey - Baseline.rds")



####  Clean Data  ####
clean <- raw %>%
  
  ## Filter TBD
  filter(
    
    position == 1 #Just undergraduate students
    
  ) %>%
  
  ## Recode and rename variables as necessary and select these variables for analysis
  transmute(
    
    ## Main analysis
    interest.selfGuided.cost = selfGuided_cost == 1 | selfGuided_cost == 2, #No %in% operator as we want to maintain NAs
    interest.selfGuided.free = selfGuided_free == 1 | selfGuided_free == 2,
    interest.teletherapy.free = teletherapy_free == 1 | teletherapy_free == 2,
    interest.teletherapy.cost = teletherapy_cost == 1 | teletherapy_cost == 2,
    age = age,
    sex = if_else(sex %in% c(1, 2), 2 - sex, NA_real_) %>% #Male or female where female is reference level (0); make intersex NA
      as.factor(),
    ethnicity = case_when(race == 1 & hispanic == 0 ~ 1, #White non-hispanic
                          race == 2 & hispanic == 0 ~ 2, #Black non-hispanic
                          race == 4 & hispanic == 0 ~ 3, #Asian non-hispanic
                          hispanic == 1             ~ 4, #Hispanic
                          T                         ~ 5) %>% #Other
      as.factor(),
    # genderMinority = case_when(genderDiff == 0 | sex == (2 - gender) ~ 0,
    #                            genderDiff == 1 & sex != (2 - gender) ~ 1,
    #                            T ~ NA_real_) %>%
    #   as.factor(),
    sexualMinority = if_else(!is.na(sexualOrientation), sexualOrientation %in% 2:9, NA) %>%
      as.numeric() %>%
      as.factor(),
    
    GAD_1, GAD_2, GAD_3, GAD_4, GAD_5, GAD_6, GAD_7,
    GAD7 = GAD_1 + GAD_2 + GAD_3 + GAD_4 + GAD_5 + GAD_6 + GAD_7 - 7, #-7 to account for original coding being off by 1
    PHQ_1, PHQ_2, PHQ_3, PHQ_4, PHQ_5, PHQ_6, PHQ_7, PHQ_8, PHQ_9,
    PHQ = PHQ_1 + PHQ_2 + PHQ_3 + PHQ_4 + PHQ_5 + PHQ_6 + PHQ_7 + PHQ_8 + PHQ_9 - 9, #-9 to account for original coding being off by 1
    
    ## Exploratory analysis
    impact = impact.edRemote + impact.jobRemote + impact.jobLoss + impact.extraHours + impact.livingSituation + impact.relativesMovedIn + impact.childcare + impact.shelterInPlace + impact.selfQuarantine + impact.mandQuarantine + impact.hadToWork + impact.reunitedWithFam + impact.illnessOfContact,
    lostIncome = incomeChange == 1 | incomeChange == 2,
    social = case_when(socialConnections == 3         ~ 0,
                       socialConnections %in% c(1, 2) ~ 1,
                       socialConnections %in% c(4, 5) ~ 2,
                       T                              ~ NA_real_),
    barrAfter.cost = barrAfter.cost / 100,
    barrAfter.availability = barrAfter.avail / 100,
    barrAfter.logistics = barrAfter.logistics / 100,
    barrAfter.myself = barrAfter.doItMyself / 100,
    barrAfter.overwhelmed = barrAfter.overwhelmed / 100,
    barrAfter.past = barrAfter.pastExperiences / 100,
    barrAfter.findOut = barrAfter.stigma / 100,
    barrAfter.notSure = barrAfter.unsureHow / 100,
    prob.anxiety = probType.anxiety,
    prob.depression = probType.depression,
    prob.aggression = probType.aggression,
    prob.attention = probType.attention,
    prob.substance = probType.substance,
    prob.autism = probType.autism,
    prob.relationship = probType.relationship,
    prob.trauma = probType.trauma,                            
    lostTreatment = supportLoss == 1 | supportLoss == 2

  )

before <- nrow(clean)

df <- clean[complete.cases(clean[,1:11]),]

after <- nrow(df)
```

# Study Overview

This study investigates interest in teletherapy and online self-guided mental health programs in
the midst of the COVID-19 pandemic among undergraduate students at a large university. The
goal of this study is to gather evidence on the extent of demand for these services during the
COVID-19 pandemic, whether it differs by individual characteristics, and whether it differs by the
characteristics of the services offered. We believe that the findings from this study can inform
public health decisions regarding the role of teletherapy and online self-help in an effective
COVID-19 response. Specifically, we seek to answer the following questions:

1. What is the extent of interest in teletherapy and online self-help during the COVID-19
pandemic among members of a large university community?
2. Does interest in teletherapy and online self-help differ by (a) sociodemographic factors
and/or (b) levels of depression and anxiety symptomatology?
3. Does interest in teletherapy and online self-help vary as a function of cost (i.e. free vs
$30/session)?

This is an exploratory study and we do not have specific hypotheses regarding the extent of
interest in teletherapy and online self-help, or whether/how interest differs across the above
conditions.

Analyses are limited to complete cases only. This drops `r before - after` of `r before` cases.

## Sample Description

```{r}
out <- data.frame(
  label = c("Age", "Sex: Female", "Sex: Male", "Ethnicity: White", "Ethnicity: Black", "Ethnicity: Asian", "Ethnicity: Hispanic", "Ethnicity: Other", "Sexual Minority: No", "Sexual Minority: Yes", "GAD", "PHQ"),
  variable = c("age", rep("sex", 2), rep("ethnicity", 5), rep("sexualMinority", 2), "GAD7", "PHQ"),
  level = c("", "0", "1", "1", "2", "3", "4", "5", "0", "1", "", ""),
  n = NA,
  pct = NA,
  mean = NA,
  sd = NA,
  stringsAsFactors = F
)

for(i in 1:nrow(out)) {
  
  if(out$variable[i] %in% c("age", "GAD7", "PHQ")) {
  
    out$n[i] <- sum(!is.na(df[[out$variable[i]]]))
    out$mean[i] <- mean(df[[out$variable[i]]])
    out$sd[i] <- sd(df[[out$variable[i]]])
  
  }
  
  if(out$variable[i] %in% c("sex", "ethnicity", "sexualMinority")) {
    
    out$n[i] <- sum(df[[out$variable[i]]] == out$level[i])
    out$pct[i] <- sum(df[[out$variable[i]]] == out$level[i]) / sum(!is.na(df[[out$variable[i]]]))

  }
  
}

out %>%
  mutate(label = gsub(".*:\\s", "", label),
         pct = percent(pct),
         mean_sd = paste0(round(mean, 2), " (", round(sd, 2), ")")) %>%
  select(label, n, pct, mean_sd) %>%
  kable(col.names = c("Variable", "n", "Proportion", "Mean (sd)"), align = "l") %>%
  column_spec(2, width = ".5in") %>%
  kableExtra::group_rows("Sex", 2, 3) %>%
  kableExtra::group_rows("Ethnicity", 4, 8) %>%
  kableExtra::group_rows("Sexual Minority", 9, 10) %>%
  kable_styling()
```

## Internal consistency

```{r}
df %>%
  select(GAD_1:GAD_7) %>%
  psych::alpha()

df %>%
  select(PHQ_1:PHQ_9) %>%
  psych::alpha()
```

# Primary Analyses

## Logistic Regression

P-values in this table are adjusted via Holm-Bonferroni method. Confidence intervals in subsequent plots aren't.

```{r}
out <- data.frame(
  label = c("All", "Age", "Sex: Female", "Sex: Male", "Ethnicity: White", "Ethnicity: Black", "Ethnicity: Asian", "Ethnicity: Hispanic", "Ethnicity: Other", "Sexual Minority: No", "Sexual Minority: Yes", "GAD", "PHQ"),
  variable = c("", "age", rep("sex", 2), rep("ethnicity", 5), rep("sexualMinority", 2), "GAD7", "PHQ"),
  level = c("", "", "0", "1", "1", "2", "3", "4", "5", "0", "1", "", ""),
  n = NA,
  stringsAsFactors = F
)

outcomes <- c("interest.selfGuided.cost", "interest.teletherapy.cost", "interest.selfGuided.free", "interest.teletherapy.free")

for(i in 1:nrow(out)) {
  
  if(out$label[i] == "All") out$n[i] <- nrow(df)
  if(out$variable[i] %in% c("age", "GAD7", "PHQ")) out$n[i] <- sum(!is.na(df[[out$variable[i]]]))
  if(out$variable[i] %in% c("sex", "ethnicity", "sexualMinority")) out$n[i] <- sum(df[[out$variable[i]]] == out$level[i])
  
}

for(outcome in outcomes) {
  
  model <- glm(data = df,
               family = "binomial",
               formula = as.formula(paste0(outcome, " ~ age + sex + ethnicity + sexualMinority + GAD7 + PHQ")))
  
  coef <- odds.ratio(model) %>%
    as.data.frame() %>%
    rownames_to_column("label") %>%
    mutate(p = p.adjust(p, "holm"),
           formattedEst = case_when(T  ~ paste0(round(OR, 2), " (p=", round(p, 3), ")")))
                                    # p < .05  ~ paste0(round(OR, 2), "* (p=", round(p, 3), ")"),
                                    # T        ~ as.character(round(OR, 2))))
  
  out[[paste0(outcome, ".pct")]] <- NA
  out[[paste0(outcome, ".OR")]] <- NA
  
  out[[paste0(outcome, ".pct")]][out$label == "All"] <- percent(mean(df[[outcome]]), accuracy = .01)
  
  for(i in 2:nrow(out)) {
    
    variable <- out$variable[i]
    level <- out$level[i]
    
    out[[paste0(outcome, ".pct")]][i] <- paste0(percent(mean(df[[outcome]][df[[variable]] == level]), accuracy = .01))
    
    if(paste0(variable, level) %in% coef$label) out[[paste0(outcome, ".OR")]][i] <- coef$formattedEst[coef$label == paste0(variable, level)]
    
  }
  
}

out %>%
  select(-variable, -level) %>%
  mutate(label = gsub(".*:\\s", "", label)) %>%
  kable(col.names = c("Variable", "n", rep(c("Percent\nInterested", "Odds Ratio"), 4)), align = "l") %>%
  add_header_above(c(" " = 2, "Self Guided (Cost)" = 2, "Teletherapy (Cost)" = 2, "Self Guided (Free)" = 2, "Teletherapy (Free)" = 2)) %>%
  column_spec(2, width = ".5in") %>%
  kableExtra::group_rows("Sex", 3, 4) %>%
  kableExtra::group_rows("Ethnicity", 5, 9) %>%
  kableExtra::group_rows("Sexual Minority", 10, 11) %>%
  kable_styling() %>%
  add_footnote(c("Odds ratios and significance flags are calculated in reference to the reference category for each variable", "Minimum sample size per cell for reporting odds ratios is 10, per pre-analysis plan", "p-values are adjusted via Holm-Bonferroni method"))
```

Notes on variable coding:

- For ethnicity, of the 63 "other," 55 are more than one race and 8 are other racial categories
- For age, there is a wide range, but limiting the age range doesn't change the results here

## Plot

All predictors are either binary or, where indicated, z-scored

Confidence intervals are not adjusted for multiple comparisons

```{r}
zScore <- function(x) {
  
  mean <- mean(x, na.rm = T)
  sd = sd(x, na.rm = T)
  
  x <- (x - mean) / sd
  
  return(x)
  
}

out.plot <- map(outcomes,
                ~ glm(data = df %>%
                        mutate(age = zScore(age),
                               GAD7 = zScore(GAD7),
                               PHQ = zScore(PHQ)),
                      family = "binomial",
                      formula = as.formula(paste0(., " ~ age + sex + ethnicity + sexualMinority + GAD7 + PHQ"))) %>%
                  odds.ratio(level = .9) %>%
                  as.data.frame() %>%
                  rownames_to_column("label") %>%
                  select(label, est = OR, lower = `5 %`, upper = `95 %`)) %>%
  set_names(outcomes) %>%
  bind_rows(.id = "model") %>%
  mutate(model = case_when(model == "interest.selfGuided.cost" ~ "Self Guided (Cost)",
                           model == "interest.teletherapy.cost" ~ "Teletherapy (Cost)",
                           model == "interest.selfGuided.free" ~ "Self Guided (Free)",
                           model == "interest.teletherapy.free" ~ "Teletherapy (Free)") %>%
           factor(levels = unique(.)),
         label = case_when(label == "age" ~ "Age (z-score)",
                           label == "sex1" ~ "Sex: Male",
                           label == "ethnicity2" ~ "Ethnicity: Black",
                           label == "ethnicity3" ~ "Ethnicity: Asian",
                           label == "ethnicity4" ~ "Ethnicity: Hispanic",
                           label == "ethnicity5" ~ "Ethnicity: Other",
                           label == "genderMinority1" ~ "Gender Minority",
                           label == "sexualMinority1" ~ "Sexual Minority",
                           label == "GAD7" ~ "GAD7 (z-score)",
                           label == "PHQ" ~ "PHQ (z-score)",
                           T ~ label) %>%
           factor(levels = rev(unique(.))))

out.plot %>%
  ggplot() +
    geom_boxplot(aes(y = label, xmiddle = est, xlower = est, xupper = est, xmin = lower, xmax = upper, color = model), stat = "identity") +
    geom_vline(xintercept = 1) +
    scale_color_discrete(name = "DV", guide = guide_legend(reverse = T)) +
    coord_cartesian(xlim = c(0, 4)) +
    scale_y_discrete(name = NULL) +
    theme_classic() +
    ggtitle("Odds Ratios")
```

# Appendix

## Exploratory Logistic Regressions

Confidence intervals are not adjusted for multiple comparisons

```{r, fig.height = 8.5}
out.plot <- map(outcomes,
                ~ glm(data = df[complete.cases(df),] %>%
                        mutate(GAD7 = zScore(GAD7),
                               PHQ = zScore(PHQ),
                               impact = zScore(impact)),
                      family = "binomial",
                      formula = as.formula(paste0(., " ~ ", paste0(names(df)[5:30], collapse = " + ")))) %>%
                  odds.ratio(level = .9) %>%
                  as.data.frame() %>%
                  rownames_to_column("label") %>%
                  select(label, est = OR, lower = `5 %`, upper = `95 %`)) %>%
  set_names(outcomes) %>%
  bind_rows(.id = "model") %>%
  mutate(model = case_when(model == "interest.selfGuided.cost" ~ "Self Guided (Cost)",
                           model == "interest.teletherapy.cost" ~ "Teletherapy (Cost)",
                           model == "interest.selfGuided.free" ~ "Self Guided (Free)",
                           model == "interest.teletherapy.free" ~ "Teletherapy (Free)") %>%
           factor(levels = unique(.)),
         label = case_when(label == "age" ~ "Age",
                           label == "sex1" ~ "Sex: Male",
                           label == "ethnicity2" ~ "Ethnicity: Black",
                           label == "ethnicity3" ~ "Ethnicity: Asian",
                           label == "ethnicity4" ~ "Ethnicity: Hispanic",
                           label == "ethnicity5" ~ "Ethnicity: Other",
                           label == "sexualMinority1" ~ "Sexual Minority",
                           label == "GAD7" ~ "GAD7 (z-score)",
                           label == "PHQ" ~ "PHQ (z-score)",
                           label == "impact" ~ "COVID-19 Impact (z-score)",
                           T ~ label) %>%
           factor(levels = rev(unique(.))))

out.plot %>%
  ggplot() +
    geom_boxplot(aes(y = label, xmiddle = est, xlower = est, xupper = est, xmin = lower, xmax = upper, color = model), stat = "identity") +
    geom_vline(xintercept = 1) +
    scale_color_discrete(name = "DV", guide = guide_legend(reverse = T)) +
    coord_cartesian(xlim = c(0, 4)) +
    scale_y_discrete(name = NULL) +
    theme_classic() +
    ggtitle("Odds Ratios - Exploratory Predictors")
```

## Interest by Ethnicity

### Overall 

```{r}
df %>%
  select_at(vars("ethnicity", matches("^interest."))) %>%
  pivot_longer(interest.selfGuided.cost:interest.teletherapy.cost) %>%
  group_by(ethnicity, name) %>%
  summarize(pct = mean(value)) %>%
  ggplot() +
    geom_bar(aes(name, pct, fill = ethnicity), stat = "identity", position = "dodge") +
    scale_fill_discrete(name = "Ethnicity", 
                        labels = c("1" = "White",
                                   "2" = "Black",
                                   "3" = "Asian", 
                                   "4" = "Hispanic",
                                   "5" = "Other")) +
    scale_x_discrete(name = NULL, 
                     limits = c("interest.selfGuided.cost", 
                                "interest.teletherapy.cost", 
                                "interest.selfGuided.free", 
                                "interest.teletherapy.free"),
                     labels = c("interest.selfGuided.cost" = "Self-Guided (Cost)",
                                "interest.selfGuided.free" = "Self-Guided (Free)",
                                "interest.teletherapy.cost" = "Teletherapy (Cost)",
                                "interest.teletherapy.free" = "Teletherapy (Free)")) +
    scale_y_continuous(name = "Percent Interested", label = scales::percent)
```

### Post-hoc Comparison: Self-Guided vs Teletherapy at Cost by Race

```{r}
for(i in 1:5) {
  
  print(i)
  
  temp <- df[df$ethnicity == i,]
  
  temp %>%
    count(teletherapy = interest.teletherapy.cost, selfGuided = interest.selfGuided.cost) %>%
    pivot_wider(names_from = selfGuided,
                names_prefix = "selfGuided",
                values_from = n) %>%
    print()
  
  mcnemar.test(temp$interest.teletherapy.cost, temp$interest.selfGuided.cost) %>%
    print()
  
}
```

## Preferences by Service Type

### Correlations Between Preferences

```{r}
matrix <- select(df,
                 `Self-Guided (Cost)` = interest.selfGuided.cost,
                 `Teletherapy (Cost)` = interest.teletherapy.cost,
                 `Self-Guided (Free)` = interest.selfGuided.free,
                 `Teletherapy (Free)` = interest.teletherapy.free) %>%
  mutate_all(as.numeric)
corTest <- cor.mtest(matrix)
matrix %>%
  cor(use = "pairwise.complete.obs") %>%
  corrplot(method = "color", 
           type = "upper", 
           insig = "label_sig", 
           tl.col = "black",
           tl.srt = 45,  
           addCoef.col = "black")
```

All correlations are significant at p < .01

### Participants by Interest in Each Service

```{r}
df %>%
  group_by(interest.selfGuided.cost, interest.teletherapy.cost, interest.selfGuided.free, interest.teletherapy.free) %>%
  summarise(n = n(),
            pct = scales::percent(n() / nrow(.))) %>%
  mutate_at(vars(matches("interest.")),
            ~ if_else(. == T, "Interested", "Not Intersted")) %>%
  rename(`Self-Guided (Cost)` = interest.selfGuided.cost,
         `Teletherapy (Cost)` = interest.teletherapy.cost,
         `Self-Guided (Free)` = interest.selfGuided.free,
         `Teletherapy (Free)` = interest.teletherapy.free) %>%
  arrange(-n) %>%
  kable(align = "l") %>%
  kable_styling()
```

### Participant Demographics by Interest

For the three largest groups identified in the table above: participants who were interested in all services, participants who weren't interested in any of the services, and participants who were interested in only the free services.

```{r}
df %>%
  mutate(interest = case_when(interest.selfGuided.cost == F &
                              interest.teletherapy.cost == F &
                              interest.selfGuided.free == T & 
                              interest.teletherapy.free == T ~ "Free Services Only",
                              interest.selfGuided.cost == T &
                              interest.teletherapy.cost == T &
                              interest.selfGuided.free == T & 
                              interest.teletherapy.free == T ~ "All Services",
                              interest.selfGuided.cost == F &
                              interest.teletherapy.cost == F &
                              interest.selfGuided.free == F & 
                              interest.teletherapy.free == F ~ "No Services",
                              T ~ "Other")) %>%
  group_by(interest) %>%
  summarize(n = n(),
            prop = n / nrow(.),
            age = mean(age),
            male = mean(sex == 1),
            white = mean(ethnicity == 1),
            black = mean(ethnicity == 2),
            asian = mean(ethnicity == 3),
            hispanic = mean(ethnicity == 4),
            other = mean(ethnicity == 5),
            sexualMinority = mean(as.numeric(sexualMinority), na.rm = T),
            GAD = mean(GAD7),
            PHQ = mean(PHQ)) %>%
  pivot_longer(n:PHQ, "Variable") %>%
  pivot_wider(names_from = interest, values_from = value) %>%
  kable(digits = 2) %>%
  add_header_above(c(" " = 1, "Respondent interested in..." = 4)) %>%
  kable_styling()
```

## Missing Data

```{r}
missmap(clean)
```
